### 2018-04-18 Old/paper_mod_save5.tex
Moving PhD paper from Dropbox to github.

\usepackage{epstopdf}
\usepackage{caption,subcaption}
\usepackage{pstricks}
\usepackage{pst-solides3d}
\usepackage{pstricks-add}
\usepackage{graphicx}
\usepackage{pst-tree}
\usepackage{pst-poly}
\usepackage{calc,ifthen}
\usepackage{float}\usepackage{multicol}
\usepackage{multirow}
\usepackage{array}
\usepackage{longtable}
\usepackage{fancyhdr}
\usepackage{algorithmicx,algpseudocode}
\usepackage{changepage}
\usepackage{color}
\usepackage{listings}
\usepackage{fancyvrb}
\usepackage{verbatim,moreverb}
\usepackage{courier}

@@

The distributed PSP auction first introduced in \cite{lazar} forms a part of the
overall market based allocation model. Consider a noncooperative game
where a set of $\mcI = \lbrace 1,\cdots,I\rbrace$ users buy a fixed
amount of resource $D_i$ from a set of resources $\mcI = \lbrace 1,\cdots,L\rbrace$. Suppose
each user $i \in \mcI$ makes a bid $s_i^l = (p_i^l, d_i^l)$ to the
seller of resource $l$,
where $p_i^l$ is the unit-price the user is willing to pay and $d_i^l$ is the
quantity the user desires. The \emph{bidding profile} forms a grid, $s \equiv
[s_i^l] \in \mcI \times \mcI$ (BAD NOTATION?
SEEMS OK)  and $s_{−i}^l \equiv [s_1^l , \cdots , s_{i−1}^l , s_{i+1}^l , \cdots
, s_I^l]_{l\in\mcI}$ is
the profile of user $i$’s opponents. In addition, the user type now includes a
\emph{routing variable}, $r_i\in\lbrace 0, 1\rbrace^L$ to manage throughput in
an arbitrary collection of nodes where $r_i^l >0$ if and only if $l(i)$ is on
$i$'s path, i.e. $l(i) \in \lbrace l\in \mcI : r_i^l >0\rbrace$. 
The market now shares $L$ resources, with allocation:
$$
    \hat{D_i^l}(y,s_{-i}^l) = \bigg\lbrack D^l -
\displaystyle\sum_{p_k^l > y, k\ne i} d_k^l\bigg\rbrack^+.
$$
The market price function (MPF) of user $i$ is defined as:
% MARKET PRICE 
\begin{align*}
    \tilde{P_i}(z, s_i) &= \displaystyle\sum_{l\in\mcI}P_i^l(z_i^l,
s_{-i}^l)r_i^l \\
    = \displaystyle\sum_{l\in\mcI}&\bigg(\inf\bigg\lbrace y\ge 0 :
\hat{D_i^l}(y,s_{-i}^l)\bigg\rbrace r_i^l\bigg),
\end{align*}
which is interpreted as the aggragate minimum price a user bids over its route in order to obtain the
resource $z$ given the opponents’ profile $s_{−i}$. Its inverse function
$\tilde{D_i}$ is defined as follows:
% INVERSE PRICE (ALLOCATION)
\begin{align*}
    \tilde{D}_i(y, s_i) &= \sup\bigg\lbrace z\in \bigg( 0,
\min_l\hat{D}_i^l/r_i^l\bigg) : \\
    &\tilde{P_i}(z,s_{-i}^l) < y\bigg\rbrace,
\end{align*}
which means the maximum available quantity at a bid price of $y$ given
$s_{−i}^j$. With this notation, the modified PSP allocation rule \cite{tuffin} is defined
as:
% ALLOCATION RULE
\begin{align*}
    \tilde{a_i}(s) &= \min\big\lbrace d_i^{l(i)}, \\
 &\frac{d_i^{l(i)}}{\sum_{k:p_k^{l(k)}=p_i^{l(i)}}d_k^{l(k)}} \tilde{D_i}(p_i^{l(i)},
s_{-i}^l)\big\rbrace,
\end{align*}
\begin{align*}
    \tilde{c_i}(s) &= \displaystyle\sum_{j\ne i}\bigg\lbrack\sum_{l\in\mcI}
p_j^{l(j)} \bigg(\tilde{a_j}(0; s_{-i}^l)\\
    &-\tilde{a_j}(s_i^l;s_{-i}^l)\bigg) r_i^l\bigg\rbrack,
\end{align*}
 $a_i^{l(i)}$ denotes the quantity user $i$ obtains by a bid price
$p_i^{l(i)}$ (when the
opponents bid $s_{−i}^l$) and the charge to user $i$ by the seller is denoted
$c_i^{l(i)}$. $\sum_{l\in\mcI} c_i^{l(i)}$ is interpreted to be the total cost incurred in the system if
user $i$ is removed from the auction. Note that the allocation rule is modified
from \cite{lazar} according to \cite{tuffin}, so that buyers with identical unit-price
$p_i$ are not rejected.

@@

% OPT-OUT BUYER
We define a \textbf{opt-out buyer} as a user $i\in\mcI$ with utility
function,
\begin{equation}\label{opt-utility}
    u_i = \theta_i \circ e_i(a) - c_i,
\end{equation}
where $e_i : [0, \infty) \rightarrow [0,\infty)$ is the expectation 
(EXPECTATION??? BAD) that user
$i$ finds a matching seller(s) $\lbrace j \rbrace$. An opt-out buyers' valuation
depends only on a scalar $e_i(a)$ which is a function of the
quantities of all the available data for sale in the secondary market.

@@

Although it is possible for a seller to fully satisfy a buyer $i$'s demand, it
is also reasonable to expect that many sellers will come close to using their
entire data cap, and only sell the fractional overage. Additionally, a buyer
will most likely not purchase fractional amounts of data, as this would incur
additional bid fees (...AND). In this case, we
determine that a buyer must coordinate their bids among multiple sellers. (SAY
MORE?) To aid in our analysis, we define, for a buyer $i$,
% MIN SET
$$
    \ell_i =\argmax_{\mcI_i' \subset \mcI_i, \vert\mcI_i'\vert =
n}\sum_{j\in\mcI_i'} d^j,
$$
where $n\in\mcI$ is chosen so that
\begin{equation}\label{minset}
    \mcI_i = \bigg\lbrace j \in  \ell_i:
\displaystyle\sum_{j\in \ell_i} d^j = d_i \bigg\rbrace.
\end{equation} 
so $\mcI_i \subset \mcI$ is the
minimal subset of sellers (which may be empty or unary) whose data is
sufficient to sum to \emph{exactly}
(DO I WANT EXACTLY? ... YES) the demand $d_i$.
Additionally, we define, for a seller $j$,
$$
    \beta^j = \bigg\lbrace i\in\mcI^j: 
d_i \le \bar{b}^j \bigg\rbrace,
$$
and so, similarly to (\ref{minset}),
% MAX SET
\begin{equation}\label{maxset}
    \mcI^j = \max_{n\in\lbrace 1,\cdots, \vert \beta_j\vert\rbrace}\bigg(\argmax_{{\mcI^j}' \subset \mcI^j,
\vert{\mcI^j}'\vert = n}\sum_{i\in{\mcI^j}'} d_i\bigg).
\end{equation}
as the maximum subset of buyers that $j$ can satisfy with budget
$\bar{b}^j$. The set $\beta^j$ is computed by $j$ before each auction (??? or
bid iteration),
i.e., for $\tau >0$, 
\begin{align*}
    \beta^{j(\tau+1)} &= \bigg\lbrace i\in\mcI^j: 
        d_i \le \bar{b}^j \bigg\rbrace, \\
    \text{where}&\\
    \bar{b}^j &= b_j - \sum_{t\in
\tau} d_i^{j(t)}
\end{align*}
and $b^j$ is $j$'s original budget.

% MECHANISM
\subsection{Data Auction Mechanism}
We may now proceed to formally define the PSP auction as a composition of the
buyers and sellers in the secondary market, along with their respective
strategies. We begin by defining the opt-out buyers' strategy.

Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$, given as
the $\alpha$-fair utility in (\ref{buyervaluation}), scaled
by a function of quantity desired from the market. 
We define, in addition to the valuation and budget of buyer $i$, a generic
\textbf{data-provisioning vector} $\vs_i$, held by buyer $i$ as part of its type. We propose the
following (novel) strategy,
{
\proposition{(Opt-out buyer strategy)}\label{strategy}
Define, for any allocation $a$,
% OPT-OUT BUYER STRATEGY
\begin{equation}\label{opt-out}
    %e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j} + a_j^i,
    e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j},
\end{equation}
and let $j^* \in \ell_i$ be the seller such that
$j^* = n \le I \in \mathcal{Z}^+$ results in a subset $\bar\mcI_i\subset\mcI$ where 
\begin{equation}\label{coordinate}
    \displaystyle\sum_{\bar\mcI_i} \frac{\min_{j\in\ell_i}(d^j)}{d_i} =
\displaystyle\sum_{\bar\mcI_i} \frac{d^{j^*}}{d_i} = d_i,
\end{equation} 
now let, 
\begin{equation}
    e_i(a) \triangleq e_i^{j^*}(a).
\end{equation}
Then, we have that $e_i$
is an optimal feasible strategy for buyer $i$.
}\\
\textbf{Proof:}
In the case that there exists a seller who can completely satisfy a buyers'
demand, $j^*=1$, and (\ref{coordinate}) holds. If such a buyer does not exist,
as the set $\ell_i$ is an ordered set, $i$ may discover seller
$j^*$ by computing $\ell_i$ iteratively. In the case that $d_i >
\sum_{j\in\mcI}d^j/d_i$, then $j^* > I$ and we consider the buyers' demand
infeasible. (WHY WE NEED A NEW RULE ... THE PARTIAL ALLOCATION RULE, ALREADY PROVEN FEASIBLE
AND TRUTHFUL)
Additionally, as the
value of the secondary market is its ability to fufill the data demands of its
users, we determine the
valuation of the transaction between seller $j$ and buyer $i$ is well-posed,
and the form of (\ref{opt-out}) is justified. We note that $\mcI_i$ is not the
possible minimum subset $\in \mcI$, but is the minimal subset where a
coordinated bid is possible.

The market price function (MPF) for a buyer in the secondary market
can now be described as follows:
% NEW MARKET PRICE
\begin{align}\label{dataprice}
\begin{split}
    \bar{P}_i&(z, s_i) =\displaystyle\sum_{j\in\mcI_i}P_i^j(z_i^j,
s_{-i}^j) \\
    &= \sum_{j\in\mcI_i}\bigg(\inf\bigg\lbrace y\ge 0 : 
    {\bar{D}_i^j}(y,s_{-i}^j)\bigg\rbrace \bigg),\\
\end{split}
\end{align}
where
% NEW ALLOCATION RULE
\begin{align}
\begin{split}\label{datacomposed}
    \bar{D}_i^j(y,s_{-i}^j) &= D_i^j(y,s_{-i}^j)\ \circ\ e_i\\
    &= \bigg\lbrack d^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+/\vs_i^j,
\end{split}
\end{align}
and is interpreted as the aggragate of minimum bid prices of buyer $i$ for bids
over $\mcI_i$ given an opponent profile $s_{-i}$.
The inverse function
% NEW INVERSE DEMAND
$\bar{D}_i$ is defined as
\begin{align}\label{datapriceinverse}
\begin{split}
    \bar{D}_i(y, s_i) &= \displaystyle\sum_{j\in\mcI_i}\bigg(\sup\bigg\lbrace z\in \big( 0,
\bar{D}_i^j \big) : \\
    &\bar{P_i}(z,s_{-i}^j) < y\bigg\rbrace\bigg).
\end{split}
\end{align}
We may interpret $\bar{D}_i(y, s_i)$ as the maximum quantity provided by the subset
$\mcI_i$ at a bid price of $y$ given $s_{-i}$. In this expression, we again note that
the price is an aggragation of the \emph{individual} prices of the buyers. As it is
possible that $\mcI_i \ne \mcI^j$, the reserve prices of the individual sellers
may vary (THIS DOES NOT GO WITH PSP THEORY!)
% DATA ALLOCATION RULE
The data allocation rule for seller $j$ is given as,
\begin{equation}\label{dataallocation}
    \bar{a}_i^j(s) = \min_{j\in\mcI_i}\bigg\lbrace d_i^j, \frac{d_i^j}{\sum_{k:p_k^j=
p_i^j}d_k^j}
\bar{D}_i^j(p_i^j,s_{-i}^j)\bigg\rbrace
\end{equation}
with cost,
\begin{align}\label{datacost}
\begin{split}
    \bar{c}_i^j(s) &= 
p^j \bigg(\bar{a}_j(0; s_{-i}^j)
    -\bar{a}_j(s_i^j;s_{-i}^j)\bigg) ,
\end{split}
\end{align}
where $\mcI_i$ is chosen as described in the buyer strategy.

The potential revenue for $j$ at unit price $y$ is determined by the
demand of the buyers. $\forall \ y\ge 0$, we determine that the demand is given by,
% BUYER DEMAND 
\begin{equation}\label{datademand}
    \rho^j(y) = \sum_{i\in\mcI_j : p_i^j\ge y} d_i^j, 
\end{equation}
with ``inverse"
% SELLER REVENUE 
\begin{equation}\label{revenue}
    f^j(z) \triangleq \sup\big\lbrace y\ge 0:
        \rho_i^j(y) \ge z \ \forall \ i \in \mcI^j\big\rbrace.
\end{equation}
For a given demand $\rho^j$, $f^j$ maps a unit of data to the highest price at
which it could be sold to any buyer $i\in \mcI^j$.
Now, in order to derive the sellers' valuation, we have the following,
{
% SELLER CONSTRAINTS
\proposition{(Seller constraints)}\label{constraints}
Let $j\in\mcI_i$ be a seller with data (budget) $b^j$.
Formalizing the quantity threshold, the seller must satisfy the quantity
constraint, $\forall \ i \in\mcI^j$,
\begin{equation}\label{quantity}
    d^j \ge d_i = e_i(a),
\end{equation}
and
\begin{equation}\label{budget}
    \displaystyle\sum_{i\in\mcI^j} e_i^j(a) \le \sum_{i\in\mcI^j} d^j_i \le b^j.
\end{equation}
In addition, for a seller who does not sell at a loss, the reserve price must
satisfy, $\forall \ i \in \mcI^j$,
\begin{equation}\label{reserveprice}
   p^j \ge \min_{i\in\mcI_j}\big({\theta_i}'(d_i^j)\big).
\end{equation}
}\\
\textbf{Proof:}
The first statement is an assumption, which we may enforce by (\ref{opt-out}),
and as a seller cannot sell more data than thier bid, (\ref{budget}) enforces
that there is a natural budget constraint for the seller. (\ref{reserveprice})
follows from the assumption that $j$ does not sell at a loss.

We may now define the seller $j$'s valuation (potential). 
{
\proposition{(Seller valuation)}\label{sellervaluation}
% SELLER VALUATION
For any $i\in\mcI^j$, 
\begin{equation}
    \theta_i^j = \int_0^{e_i^j(a)} f^j(z) \ dz.
\end{equation}
it follows that 
\begin{equation}\label{valuation}
    \theta^j = \displaystyle\sum_{i\in\mcI^j}
 \int_0^{e_i^j(a)} f^j(z) \ dz.
\end{equation}
}
\textbf{Proof:} 
We assume that a seller will try to maximize profit, and
so there is an incentive sell all its data, so from Lemma
\ref{sellervaluation},  $\sum_{i\in{\mcI^j}} d_i^j = 
\sum_{i\in\mcI^j} e_i$,
The remainder of the proof follows as in \cite{semret}.
The sellers' natural utility is the potential
profit $u^j = \theta^j\circ e$, where $\theta^j$ is the
potential revenue from the sale of data composed with opt-out value
$e_i(a)$ for each buyer $i$ that has $j$ in its set of qualified buyers
$\mcI^j$. Note that we have chosen to omit the original cost of the data
paid to the ISP, as a discussion of mobile data plans is outside the scope of this
paper. This is intuitive as a seller who does not meet the demand of \emph{any} buyer will not
participate in any auction.

We claim that there is an incentive for the seller to
accept fractional bids (i.e. sell fraction of thier data $d^j$). Reasonably,
there may not exist a buyer such that $d_i = d^j$, in addition, a seller may accept
fractional bids in order to
maximize the revenue gained per unit of data sold over time.
Finally, in the case that the seller does not know the exact amount of
leftover data available, then they may only sell enough data to ensure that
they will not become a buyer while they submit their total data overage to the
secondary market. (FUTURE WORK?)
% SELLER INCENTIVE
{
\lemma{(Seller incentive)}\label{incentive}
Let $j$ be a buyer with fixed price $p^j$. Then, in order for $j$ to change its
quantity $d^j$ we must have, for some $i \in \mcI^j$,
\begin{equation}
       p_i^j \ge p^j \qquad \text{and} \qquad d_i^j < d^j.
\end{equation}
}
\textbf{Proof:}
We will show that if the Lemma holds, then $j$
(NEED TO THINK... NEED THIS OR FUTURE WORK?)\\

The main contribution of this work is comprised by these rules, which we use to
describe an auction mechanism inspired by the classic PSP throughput problem. In order to apply PSP to the data-sharing secondary market described in
\cite{zheng} the idea of a ``route" is repurposed. We claim that in the
data-sharing model, it is not necessary to bid on a minimal route, and that our
formulation not only holds the desired VCG qualities, but minimizes the message
space and auction duration, resulting in a faster convergence time than the
classic throughput problem (EEEK!).

>>>>

\usepackage{epstopdf}
\usepackage{caption,subcaption}
\usepackage{pstricks}
\usepackage{pst-solides3d}
\usepackage{pstricks-add}
\usepackage{graphicx}
\usepackage{pst-tree}
\usepackage{pst-poly}
\usepackage{calc,ifthen}
\usepackage{float}\usepackage{multicol}
\usepackage{multirow}
\usepackage{array}
\usepackage{longtable}
\usepackage{fancyhdr}
\usepackage{algorithmicx}
\usepackage[noend]{algpseudocode}
\usepackage{changepage}
\usepackage{color}
\usepackage{listings}
\usepackage{fancyvrb}
\usepackage{verbatim,moreverb}
\usepackage{courier}
\usepackage{algorithm}

@@

The distributed PSP auction first introduced in \cite{lazar} forms a part of the
overall market based allocation model. Consider a noncooperative game
where a set of $\mcI = \lbrace 1,\cdots,I\rbrace$ users buy a fixed
amount of resource $D_i$ from a set of resources $\mcI = \lbrace 1,\cdots,L\rbrace$. Suppose
each user $i \in \mcI$ makes a bid $s_i^l = (p_i^l, d_i^l)$ to the
seller of resource $l$,
where $p_i^l$ is the unit-price the user is willing to pay and $d_i^l$ is the
quantity the user desires. The \emph{bidding profile} forms a grid, $s \equiv
[s_i^l] \in \mcI \times \mcI$ (BAD NOTATION?
SEEMS OK)  and $s_{−i}^l \equiv [s_1^l , \cdots , s_{i−1}^l , s_{i+1}^l , \cdots
, s_I^l]_{l\in\mcI}$ is
the profile of user $i$’s opponents. In addition, the user type now includes a
\emph{routing variable}, $r_i\in\lbrace 0, 1\rbrace^L$ to manage throughput in
an arbitrary collection of nodes where $r_i^l >0$ if and only if $l(i)$ is on
$i$'s path, i.e. $l(i) \in \lbrace l\in \mcI : r_i^l >0\rbrace$. 
The market now shares $L$ resources, with allocation:
$$
    \hat{D_i^l}(y,s_{-i}^l) = \bigg\lbrack D^l -
\displaystyle\sum_{p_k^l > y, k\ne i} d_k^l\bigg\rbrack^+.
$$
The market price function (MPF) of user $i$ is defined as:
% MARKET PRICE 
\begin{align*}
    \tilde{P_i}(z, s_{-i}) &= \displaystyle\sum_{l\in\mcI}P_i^l(z_i^l,
s_{-i}^l)r_i^l \\
    = \displaystyle\sum_{l\in\mcI}&\bigg(\inf\bigg\lbrace y\ge 0 :
\hat{D_i^l}(y,s_{-i}^l)\bigg\rbrace r_i^l\bigg),
\end{align*}
which is interpreted as the aggragate minimum price a user bids over its route in order to obtain the
resource $z$ given the opponents’ profile $s_{−i}$. Its inverse function
$\tilde{D_i}$ is defined as follows:
% INVERSE PRICE (ALLOCATION)
\begin{align*}
    \tilde{D}_i(y, s_{-i}) &= \sup\bigg\lbrace z\in \bigg( 0,
\min_l\hat{D}_i^l/r_i^l\bigg) : \\
    &\tilde{P_i}(z,s_{-i}^l) < y\bigg\rbrace,
\end{align*}
which means the maximum available quantity at a bid price of $y$ given
$s_{−i}^j$. With this notation, the modified PSP allocation rule \cite{tuffin} is defined
as:
% ALLOCATION RULE
\begin{align*}
    \tilde{a_i}(s) &= \min\big\lbrace d_i^{l(i)}, \\
 &\frac{d_i^{l(i)}}{\sum_{k:p_k^{l(k)}=p_i^{l(i)}}d_k^{l(k)}} \tilde{D_i}(p_i^{l(i)},
s_{-i}^l)\big\rbrace,
\end{align*}
\begin{align*}
    \tilde{c_i}(s) &= \displaystyle\sum_{j\ne i}\bigg\lbrack\sum_{l\in\mcI}
p_j^{l(j)} \bigg(\tilde{a_j}(0; s_{-i}^l)\\
    &-\tilde{a_j}(s_i^l;s_{-i}^l)\bigg) r_i^l\bigg\rbrack,
\end{align*}
 $a_i^{l(i)}$ denotes the quantity user $i$ obtains by a bid price
$p_i^{l(i)}$ (when the
opponents bid $s_{−i}^l$) and the charge to user $i$ by the seller is denoted
$c_i^{l(i)}$. $\sum_{l\in\mcI} c_i^{l(i)}$ is interpreted to be the total cost incurred in the system if
user $i$ is removed from the auction. Note that the allocation rule is modified
from \cite{lazar} according to \cite{tuffin}, so that buyers with identical unit-price
$p_i$ are not rejected.

@@

% OPT-OUT BUYER
We define a \textbf{opt-out buyer} as a user $i\in\mcI$ with utility
function,
\begin{equation}\label{opt-utility}
    u_i = \theta_i \circ e_i(a) - c_i,
\end{equation}
where $e_i : [0, \infty) \rightarrow [0,\infty)$ is the expectation 
(EXPECTATION??? BAD) that user
$i$ finds matching seller(s). An opt-out buyers' valuation
depends only on a scalar $e_i(a)$ which is a function of the
quantities of all the available data for sale in the secondary market.

@@

Although it is possible for a seller to fully satisfy a buyer $i$'s demand, it
is also reasonable to expect that many sellers will come close to using their
entire data cap, and only sell the fractional overage. In this case, we
determine that a buyer must coordinate their bids among multiple sellers. (SAY
MORE?) Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$, given as
the $\alpha$-fair utility in (\ref{buyervaluation}), scaled
by a function of quantity desired from the market. 
We define, in addition to the valuation and budget of buyer $i$, a generic
\textbf{data-provisioning vector} $\vs_i$, held by buyer $i$ as part of its type.
Define, for any allocation $a$,
% OPT-OUT BUYER STRATEGY
\begin{equation}\label{opt-out}
    %e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j} + a_j^i,
    e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j},
\end{equation}
and define,
% MIN SET
$$
    \ell_i =\argmax_{\mcI_i' \subset \mcI_i, \vert\mcI_i'\vert =
n}\sum_{j\in\mcI_i'} d^j.
$$
Let $j^* \in \ell_i$ be the seller such that
$j^* = n \le I \in \mathcal{Z}^+$ results in a minimal subset $\bar\mcI_i\subset\mcI$ where 
\begin{equation}\label{coordinate}
    \displaystyle\sum_{\bar\mcI_i} \frac{\min_{j\in\ell_i}(d^j)}{d_i} =
\displaystyle\sum_{\bar\mcI_i} \frac{d^{j^*}}{d_i} = d_i.
\end{equation} 
Now let, 
\begin{equation}\label{opt-quantity}
    e_i(a) \triangleq e_i^{j^*}(a).
\end{equation}
% EXACTING STRATEGY, SAVE JUST IN CASE
\iffalse
where $n\in\mcI$ is chosen so that
\begin{equation}\label{minset}
    \mcI_i = \bigg\lbrace j \in  \ell_i:
\displaystyle\sum_{j\in \ell_i} d^j = d_i \bigg\rbrace.
\end{equation} 
so $\mcI_i \subset \mcI$ is the
minimal subset of sellers (which may be empty or unary) whose data is
sufficient to sum to \emph{exactly}
(DO I WANT EXACTLY? ... YES) the demand $d_i$.
\fi
We note that in the case that there exists a seller who can completely satisfy a buyers'
demand, $j^*=1$, and (\ref{coordinate}) holds. If such a buyer does not exist,
as the set $\ell_i$ is an ordered set, $i$ may discover 
$j^*$ by computing $\ell_i$. In the case that $d_i >
\sum_{j\in\mcI}d^j/d_i$, then $j^* > I$ and we consider the buyers' demand
infeasible. (WHY WE NEED A NEW RULE ... THE PARTIAL ALLOCATION RULE, ALREADY PROVEN FEASIBLE
AND TRUTHFUL)
Additionally, as the
value of the secondary market is its ability to fufill the data demands of its
users, we determine the
valuation of the transaction between seller $j$ and buyer $i$ is well-posed,
and the form of (\ref{opt-quantity}) is justified. We also note that $\mcI_i$ is not the
possible minimum subset $\in \mcI$ able to satisfy $i$'s demand, it is the minimal subset where a
coordinated bid is possible.

It is necessary that we determine there is an incentive for the seller to
accept fractional bids (i.e. sell fraction of thier data $d^j$). Reasonably,
there may not exist a buyer such that $d_i = d^j$, in addition, a seller may accept
fractional bids in order to
maximize the revenue gained per unit of data by increasing market competition
(NEED CITE!).
Finally, in the case that the seller does not know the exact amount of
leftover data available, then they may only sell enough data to ensure that
they will not become a buyer while they submit their total data overage to the
secondary market. (FUTURE WORK?)
(NOT SURE IF WE CAN ALLOCATE ON-THE-FLY AND HAVE MARKET EQ...)
Define, for a seller $j$, the maximum subset of buyers that $j$ can satisfy its
budget,
% MAX SET
\begin{equation}\label{maxset}
    \mcI^j = \lbrace i\in\mcI : j \in \mcI_i\rbrace.
    %\mcI^j = \max_{n\in\lbrace 1,\cdots, \vert \beta_j\vert\rbrace}\bigg(\argmax_{{\mcI^j}' \subset \mcI^j,
    %\vert{\mcI^j}'\vert = n}\sum_{i\in{\mcI^j}'} d_i\bigg).
\end{equation}
\iffalse
The set $\beta^j$ is computed by $j$ before each
bid iteration. Suppose the auction duration is $\tau \in (0, \infty)$.
For $t \in (0,\tau]$, 
$$
    \beta^{j(t+1)} = \bigg\lbrace i\in\mcI^j: d_i \le \bar{b}^j \bigg\rbrace, \\
$$
\fi
Let the winner be determined by,
\iffalse %SAVING IN CASE ITERATIVELY ASSIGNING DATA DOES NOT WORK
$$
    \ell_i =\argmax_{\mcI_i' \subset \mcI_i, \vert\mcI_i'\vert =
n}\sum_{j\in\mcI_i'} d^j.
$$
Let $j^* \in \ell_i$ be the seller such that
$j^* = n \le I \in \mathcal{Z}^+$ results in a minimal subset $\bar\mcI^j\subset\mcI$ where 
\begin{equation}
    \displaystyle\sum_{\bar\mcI^j} d_i^j = b^j.
\end{equation} 
\fi
\begin{equation}\label{winner}
    \bar{i} = \displaystyle\argmax_{I^j}\sum_{i\in I^j} p_i^j.
\end{equation}
\iffalse
and so,
$$
    \bar{b}^{j(t+1)} = b^{j(t)} - \sum_{\bar{i}\in\mcI^j} d_{i^*}^{j(t)},
$$
\fi
Also define
$$
    \ell^j =\argmax_{{\mcI^j}' \subset \mcI^j, \vert{\mcI^j}'\vert =
n}\sum_{i\in{\mcI^j}'} p_i^j,
$$
and let $i^* \in \ell^j$ be the buyer such that
$i^* = n \le I \in \mathcal{Z}^+$ results in a minimal subset $\bar\mcI^j\subset\mcI$ where 
\begin{equation}
    \displaystyle\sum_{i\in\bar\mcI^j} d_i^j > b^j.
\end{equation} 
Finally, define $j$'s reserve price as, 
\begin{equation}\label{newprice}
    p^j = \theta_{i^*}'(d_{i^*}^j) + \epsilon.
\end{equation}
The potential revenue for $j$ at unit price $y$ is determined by the
demand of the buyers. $\forall \ y\ge 0$, the demand is given by,
% BUYER DEMAND 
\begin{equation}\label{datademand}
    \rho^j(y) = \sum_{i\in\mcI_j : p_i^j\ge y} d_i^j, 
\end{equation}
with ``inverse"
% SELLER REVENUE 
\begin{equation}\label{revenue}
    f^j(z) \triangleq \sup\big\lbrace y\ge 0:
        \rho_i^j(y) \ge z \ \forall \ i \in \mcI^j\big\rbrace.
\end{equation}
For a given demand $\rho^j$, $f^j$ maps a unit of data to the highest price at
which it could be sold to any buyer $i\in \mcI^j$.
Now, in order to derive the sellers' valuation, we have the following,
{
% SELLER CONSTRAINTS
\lemma{(Seller constraints)}\label{constraints}
Let $j\in\mcI_i$ be a seller with data (budget) $b^j$.
Formalizing the quantity threshold, the seller must satisfy the quantity
constraint, $\forall \ i \in\mcI^j$,
\begin{equation}\label{quantity}
    d^j \ge d_i = e_i(a),
\end{equation}
and
\begin{equation}\label{budget}
    \displaystyle\sum_{i\in\mcI^j} e_i^j(a) \le \sum_{i\in\mcI^j} d^j_i \le b^j.
\end{equation}
In addition, for a seller who does not sell at a loss, the reserve price must
satisfy, $\forall \ i \in \mcI^j$,
\begin{equation}\label{reserveprice}
   p^j \ge \min_{i\in\mcI^j}\big({\theta_i}'(d_i^j)\big).
\end{equation}
}\\
\textbf{Proof:}
The first statement is an assumption, which we may enforce by (\ref{opt-out}),
and as a seller cannot sell more data than thier bid, (\ref{budget}) enforces
that there is a natural budget constraint for the seller. (\ref{reserveprice})
follows from the assumption that $j$ does not sell at a loss.

We may now define the seller $j$'s valuation (potential). 
{
\lemma{(Seller valuation)}\label{sellervaluation}
% SELLER VALUATION
For any $i\in\mcI^j$, 
\begin{equation}
    \theta_i^j = \int_0^{e_i^j(a)} f^j(z) \ dz.
\end{equation}
it follows that 
\begin{equation}\label{valuation}
    \theta^j = \displaystyle\sum_{i\in\mcI^j}
 \int_0^{e_i^j(a)} f^j(z) \ dz.
\end{equation}
}
\textbf{Proof:} 
We assume that a seller will try to maximize profit, and
so there is an incentive sell all its data, so from Lemma
\ref{sellervaluation},  $\sum_{i\in{\mcI^j}} d_i^j = 
\sum_{i\in\mcI^j} e_i$,
The remainder of the proof follows as in \cite{semret}.
The sellers' natural utility is the potential
profit $u^j = \theta^j\circ e$, where $\theta^j$ is the
potential revenue from the sale of data composed with opt-out value
$e_i(a)$ for each buyer $i\in\mcI^j$. Note that we have chosen to omit the original cost of the data
paid to the ISP, as a discussion of mobile data plans is outside the scope of this
paper. This is intuitive as a seller who does not meet the demand of \emph{any} buyer will not
participate in any auction.

% MECHANISM
\subsection{Data Auction Mechanism}
We may now proceed to formally define the PSP auction as a composition of the
buyers and sellers in the secondary market. 
The market price function (MPF) for a buyer in the secondary market
can now be described as follows:
% NEW MARKET PRICE
\begin{align}\label{dataprice}
\begin{split}
    \bar{P}_i&(z, s_{-i}) =\displaystyle\sum_{j\in\mcI_i}P_i^j(z_i^j,
s_{-i}^j) \\
    &= \sum_{j\in\mcI_i}\bigg(\inf\bigg\lbrace y\ge 0 : 
    {\bar{D}_i^j}(y,s_{-i}^j)\bigg\rbrace \bigg),\\
\end{split}
\end{align}
where
% NEW ALLOCATION RULE
\begin{align}
\begin{split}\label{datacomposed}
    \bar{D}_i^j(y,s_{-i}^j) &= D_i^j(y,s_{-i}^j)\ \circ\ e_i\\
    &= \bigg\lbrack d^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+/\vs_i^j,
\end{split}
\end{align}
and is interpreted as the aggragate of minimum bid prices of buyer $i$ for bids
over $\mcI_i$ given an opponent profile $s_{-i}$.
The inverse function
% NEW INVERSE DEMAND
$\bar{D}_i$ is defined as
\begin{align}\label{datapriceinverse}
\begin{split}
    \bar{D}_i(y, s_{-i}) &= \displaystyle\sum_{j\in\mcI_i}\bigg(\sup\bigg\lbrace z\in \big( 0,
\bar{D}_i^j \big) : \\
    &\bar{P_i}(z,s_{-i}^j) < y\bigg\rbrace\bigg).
\end{split}
\end{align}
We may interpret $\bar{D}_i(y, s_i)$ as the maximum quantity provided by the subset
$\mcI_i$ at a bid price of $y$ given $s_{-i}$. In this expression, we again note that
the price is an aggragation of the \emph{individual} prices of the buyers. As it is
possible that $\mcI_i \ne \mcI^j$, the reserve prices of the individual sellers
may vary (THIS DOES NOT GO WITH PSP THEORY!)
% DATA ALLOCATION RULE
The data allocation rule is given as,
\begin{align}\label{dataallocation}
\begin{split}
    \bar{a}_i(s) &= a_i(s) \circ e_i =
\displaystyle\sum_{j\in\mcI_i}\bigg(\min\bigg\lbrace d_i^j/\vs_i^j,
\\
    &\frac{d_i^j}{\sum_{k:p_k^j=
p_i^j}d_k^j}
\bar{D}_i^j(p_i^j,s_{-i}^j)\bigg\rbrace\bigg)
\end{split}
\end{align}
with cost to the buyer,
% DATA COST
\begin{align}\label{datacost}
\begin{split}
    \bar{c}_i(s) &= \displaystyle\sum_{j\in\mcI_i} 
p^j \bigg(\bar{a}_j(0; s_{-i}^j)
    -\bar{a}_j(s_i^j;s_{-i}^j)\bigg).
\end{split}
\end{align}

The main contribution of this work is comprised by the modified PSP rules,
along with the user strategies, which we use to
describe an auction mechanism inspired by the classic PSP throughput problem. In order to apply PSP to the data-sharing secondary market described in
\cite{zheng} the idea of a ``route" is repurposed, and by the use of the
opt-out buyer, we are abel to achieve a market equilibrium. We claim that in
the secondary market our
formulation not only holds the desired VCG qualities, but minimizes the message
space and auction duration, resulting in a convergence time (FIND COMPETITVE RATIO?)
with respect to the classic throughput problem.
